Plots_manuscript_v0.3

### 2020-07-25 R/Plots_manuscript_v0.3.Rmd
Fix phenotypes for 4WCR and plot FL and GR as functions of weather

# Load data
Add any data that needs to be loaded for these analyses here.
```{r}
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
metadata <- read_rds(file.path(workingdir, "data", "metadata.rds"))
sites <- read_rds(file.path(workingdir, "data", "sites.rds"))
subpops <- read_rds(file.path(workingdir, "data", "subpop_color_coding.rds"))
phe_gr_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_GR50.rds"))
phe_fl_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_FL50.rds"))
phenotypes <- readRDS("~/Github/pvdiv-phenology-gxe/data/Julian_date_GDD_and_rainfall_phenotypes_4wcr_and_gwas.rds")
h2fl <- read_csv("~/Github/pvdiv-phenology-gxe/analysis/heritability/h2_df_FL50_related_functions_of_weather_v3.csv")
h2gr <- read_csv("~/Github/pvdiv-phenology-gxe/analysis/heritability/h2_df_GR50_related_functions_of_weather_v2.csv")
```

@@

## h2 flowering weather
```{r}
flh2 <- h2fl %>%
  filter(phe %in% c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl", "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d", "crain_7d")) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "all",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "all",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "GR50" ~ "50% greenup",
                              phe == "FL50" ~ "50% flowering",
                              TRUE ~ phe))
flh2$site <- factor(flh2$site, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "all", "nine_sites"))
flh2$phe_name <- factor(flh2$phe_name, levels = c("50% greenup", "50% flowering"))
flh2$subpop_name <- factor(flh2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "all"))

flh2_p1 <- flh2 %>%
  filter(subpop == "Gulf" & !(site %in% c("nine_sites")) & !is.na(site)) %>%
  ggplot(aes(x = phe, y = Estimate)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  facet_wrap(~ site) +
  geom_hline(data = filter(flh2, subpop == "Gulf" & !(site %in% c("NA", "nine_sites")) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + ylim(c(0, 1))
save_plot("../manuscript/plots/h2_FL_site_weather_functions.png", plot = flh2_p1, base_height = 3.5, base_asp = 1.618)
flh2 %>%
  filter(subpop == "Gulf_and_Midwest" & !(site %in% c("eight_sites", "nine_sites")) & !is.na(site)) %>%
  ggplot(aes(x = phe, y = Estimate)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  facet_wrap(~ site) +
  geom_hline(data = filter(flh2, subpop == "Gulf_and_Midwest" & !(site %in% c("NA", "nine_sites")) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + ylim(c(0,1))

```
## h2 greenup weather
```{r}

h2gr$site <- factor(h2gr$site, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD"))
flh2 %>%
  filter(subpop == "Gulf" & !(site %in% c("eight_sites", "nine_sites")))

grh2_p1 <- h2gr %>%
  filter(subpop == "Gulf" & !(site %in% c("eight_sites", "nine_sites")) & !is.na(site)) %>%
  ggplot(aes(x = phe, y = Estimate)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  facet_wrap(~ site) +
  geom_hline(data = filter(flh2, subpop == "Gulf" & !(site %in% c("NA", "nine_sites")) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + ylim(c(0, 1))
save_plot("../manuscript/plots/h2_GR_site_weather_functions.png", plot = grh2_p1, base_height = 3.5, base_asp = 1.618)
```
## Phenotype correlations
can you easily look at the correlation between greenup ranks at OK versus NE?
```{r}
phe_gr_df %>%
  filter(SITE %in% c("LINC", "STIL")) %>%
  ungroup() %>%
  select(PLANT_ID:GR50, -PLOT_GL) %>%
  pivot_wider(names_from = "SITE", values_from = "GR50", values_fn = mean) %>%
  ggplot(aes(x = STIL, y = LINC)) +
  geom_hex() + #aes(color = SUBPOP), height = 1, width = 1) +
  scale_fill_viridis(option = "B",
                     end = 0.9, direction = -1)

@@

## ASReml h2 greenup analysis
```{r}
library(tidyverse)
library(asreml)
library(switchgrassGWAS)
library(cowplot)
```

```{r}
source("~/Github/Functions_ggplot-theme-adjustments_2018-01-03.R")
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
outputdir <- file.path(workingdir, "analysis", "heritability")
metadata <- read_rds(file.path(workingdir, "data", "metadata.rds"))
sites <- read_rds(file.path(workingdir, "data", "sites.rds"))
subpops <- read_rds(file.path(workingdir, "data", "subpop_color_coding.rds"))
phe_gr_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_GR50.rds"))
phe_fl_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_FL50.rds"))
k_full <- read_rds("~/Github/pvdiv-genome/tensite_twoyear/Kinship_van_Raden_630_individuals_SNPs_r2_20percent.rds")

@@

## Include just texas sites for greenup and just northern four sites.
```{r}
site_v <- list(TX1 = "TX1", TX2 = "TX2", TX3 = "TX3", OK = "OK", MO = "MO",
               NE = "NE", IL = "IL", MI = "MI", SD = "SD", eight_sites = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD"), nine_sites = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD"), tx_sites = c("TX1", "TX2", "TX3"), north_sites = c("MO", "NE", "MI", "SD"))
subpop_v <- list(Gulf = "Gulf", Midwest = "Midwest", Gulf_and_Midwest = c("Gulf", "Midwest"), Atlantic = "Atlantic", three_subpops = c("Atlantic", "Gulf", "Midwest"))
phe_fl <- c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl",
           "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d",
           "crain_7d")
phe_gr <- c("GR50", "DYLN", "cgdd_12c_jan2gr", "cgdd_8c_jan2gr", "tmax_18d", 
            "tmin_18d", "tave_18d", "cgdd_12c_18d", "tmax_10d", "tmin_10d",
            "tave_10d", "cgdd_12c_10d", "tmax_5d", "tmin_5d", "tave_5d",
            "cgdd_12c_5d")
phe_dfs <- list(phe_gr_df, phe_fl_df)
phe_lists <- list(phe_gr, phe_fl)
h2_table <- tibble()

for(p in 1){#seq_along(phe_dfs)){
  phe_v <- phe_lists[[p]]
  phe <- phe_dfs[[p]]

  for(i in 12:13){#seq_along(site_v)){
    for(j in 1:3){#seq_along(subpop_v)){
      for(k in seq_along(phe_v)){
        phe_single <- phe %>%
    left_join(sites, by = "SITE") %>%
    filter(manu_site %in% site_v[[i]] & SUBPOP %in% subpop_v[[j]]) %>%
    rename(phenotype = eval(phe_v[k])) %>%
    mutate(PLANT_ID = as_factor(PLANT_ID),
           SITE = as_factor(SITE),
           PLOT_GL = as_factor(PLOT_GL)) %>%
    as.data.frame()

  if(length(site_v[[i]]) > 1){  # need to add site as a random factor if 
    # there is more than one site included in the dataset.
    tryCatch({
     asr_out <- asreml(phenotype ~ 1,
                       random = ~vm(PLANT_ID, k_full) +
                         ~idv(SITE), #:vm(PLANT_ID, k_full),
                       residual = ~idv(units),
                       data = phe_single, 
                       workspace = "3gb")

@@

  if(i == 1 & j == 1 & k == 1){
    h2_table <- h2_est
  } else {
    h2_table <- add_row(h2_table, h2_est)
  }
  tryCatch({
      save_plot(filename=file.path(outputdir, paste0("ASReml_performance_",
                                                 names(site_v)[i], "_",
                                                 names(subpop_v)[j],
                                                 "_", phe_v[k], ".png")), 
            plot = plot(asr_out))
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})

>>>>

# Load data
Add any data that needs to be loaded for these analyses here.
```{r}
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
metadata <- read_rds(file.path(workingdir, "data", "metadata.rds"))
sites <- read_rds(file.path(workingdir, "data", "sites.rds"))
subpops <- read_rds(file.path(workingdir, "data", "subpop_color_coding.rds"))
phe_gr_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_GR50.rds"))
phe_fl_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_FL50.rds"))
phenotypes <- readRDS("~/Github/pvdiv-phenology-gxe/data/Julian_date_GDD_and_rainfall_phenotypes_4wcr_and_gwas.rds")
h2fl <- read_csv("~/Github/pvdiv-phenology-gxe/analysis/heritability/h2_df_FL50_related_functions_of_weather_v3.csv")
h2gr <- read_csv("~/Github/pvdiv-phenology-gxe/analysis/heritability/h2_df_GR50_related_functions_of_weather_v2.csv")
h2gr4 <- read_csv(file.path(workingdir, "analysis", "heritability", "h2_df_GR50_related_functions_of_weather_v4.csv"))
h2gr <- h2gr %>%
  full_join(h2gr4)
```

@@

## h2 flowering weather
```{r}
flh2 <- h2fl %>%
  filter(phe %in% c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl", "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d", "crain_7d")) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "All",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "all",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "FL50" ~ "50% flowering",
                              phe == "dyln_fl50" ~ "daylength",
                              phe == "dyln_change_sec" ~ "daylength change (s)",
                              phe == "cgdd_12c_gr2fl" ~ "GDD, GR to FL",
                              phe == "crain_gr2fl" ~ "Rainfall, GR to FL",
                              phe == "crain_1d" ~ "Rainfall, 1 day",
                              phe == "crain_2d" ~ "Rainfall, 2d sum",
                              phe == "crain_3d" ~ "Rainfall, 3d sum",
                              phe == "crain_5d" ~ "Rainfall, 5d sum",
                              phe == "crain_7d" ~ "Rainfall, 7d sum",
                              TRUE ~ phe))
flh2$site <- factor(flh2$site, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "nine_sites"))
flh2$phe_name <- factor(flh2$phe_name, levels = c("50% flowering", "daylength",
                                                  "daylength change (s)",
                                                  "GDD, GR to FL",
                                                  "Rainfall, GR to FL",
                                                  "Rainfall, 1 day",
                                                  "Rainfall, 2d sum",
                                                  "Rainfall, 3d sum",
                                                  "Rainfall, 5d sum",
                                                  "Rainfall, 7d sum"
                                                  ))
flh2$subpop_name <- factor(flh2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "all"))
site_plot <- c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD", "All", "Texas", "North")

flh2_p1 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 1.1)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)

save_plot("../manuscript/plots/h2_FL_site_weather_functions_All_Sites_v2.png", plot = flh2_p1, base_height = 7, base_asp = 1.3)

site_plot <- c("All", "Texas", "North")

flh2_p2 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.5)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")

save_plot("../manuscript/plots/h2_FL_site_weather_functions_All_Sites_v2.png", plot = flh2_p2, base_height = 4, base_asp = 1.5)
```
## h2 greenup weather
```{r}
h2gr
```

```{r}
unique(h2gr$site)
grh2 <- h2gr %>%
  filter(!(phe %in% c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl", "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d", "crain_7d", "DYLN"))) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "All",
                          site == "tx_sites" ~ "Texas",
                          site == "north_sites" ~ "North",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "All",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "GR50" ~ "50% greenup",
                              phe == "FL50" ~ "50% flowering",
                              phe == "cgdd_12c_jan2gr" ~ "GDD 01-01 to greenup",
                              phe == "cgdd_8c_jan2gr" ~ "GDD 8C 01-01 to greenup",
                              phe == "tmax_18d" ~ "Max T, 18d mean",
                              phe == "tmin_18d" ~ "Min T, 18d mean",
                              phe == "tave_18d" ~ "Mean T, 18d mean",
                              phe == "tmax_10d" ~ "Max T, 10d mean",
                              phe == "tmin_10d" ~ "Min T, 10d mean",
                              phe == "tave_10d" ~ "Mean T, 10d mean",
                              phe == "tmax_5d" ~ "Max T, 5d mean",
                              phe == "tmin_5d" ~ "Min T, 5d mean",
                              phe == "tave_5d" ~ "Mean T, 5d mean",
                              phe == "cgdd_12c_10d" ~ "GDD, 10d",
                              phe == "cgdd_12c_18d" ~ "GDD, 18d",
                              phe == "cgdd_12c_5d" ~ "GDD, 5d",
                              TRUE ~ phe))
grh2$site <- factor(grh2$site, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "Texas", "North", "nine_sites"))
grh2$phe_name <- factor(grh2$phe_name, levels = c("50% greenup", "GDD, 5d",
                                                  "Min T, 5d mean",
                                                  "Mean T, 5d mean",
                                                  "Max T, 5d mean",
                                                  "GDD, 10d",
                                                  "Min T, 10d mean",
                                                  "Mean T, 10d mean",
                                                  "Max T, 10d mean",
                                                  "GDD, 18d",
                                                  "Min T, 18d mean",
                                                  "Mean T, 18d mean",
                                                  "Max T, 18d mean",
                                                  "GDD 8C 01-01 to greenup",
                                                  "GDD 01-01 to greenup"))
grh2$subpop_name <- factor(grh2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "All"))

subpop_v <- list(Gulf = "Gulf", Midwest = "Midwest", Gulf_and_Midwest = c("Gulf", "Midwest"), Atlantic = "Atlantic", three_subpops = c("Atlantic", "Gulf", "Midwest"))
i=3
subpop_v[[i]]
site_plot <- c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "Texas", "North")

grh2_p1 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 1.1)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_v2.png", plot = grh2_p1, base_height = 7, base_asp = 1.3)

site_plot <- c( "All", "Texas", "North")

grh2_p2 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.5)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_v3.png", plot = grh2_p2, base_height = 5, base_asp = 1.5)

site_plot <- c( "All")

grh2_p3 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.15)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_v4.png", plot = grh2_p3, base_height = 4, base_asp = 1.5)

gr_fl_p1 <- plot_grid(grh2_p3, flh2_p2, nrow = 2)
```
## Phenotype correlations
can you easily look at the correlation between greenup ranks at OK versus NE?
```{r}
phe_gr_df %>%
  filter(SITE %in% c("LINC", "STIL")) %>%
  ungroup() %>%
  select(PLANT_ID:GR50, -PLOT_GL) %>%
  pivot_wider(names_from = "SITE", values_from = "GR50", values_fn = mean) %>%
  ggplot(aes(x = STIL, y = LINC)) +
  geom_hex() + #aes(color = SUBPOP), height = 1, width = 1) +
  scale_fill_viridis(option = "B",
                     end = 0.9, direction = -1)

@@

## ASReml h2 greenup analysis
```{r}
library(tidyverse)
library(asreml)
library(switchgrassGWAS)
library(cowplot)

source("~/Github/Functions_ggplot-theme-adjustments_2018-01-03.R")
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
outputdir <- file.path(workingdir, "analysis", "heritability")
metadata <- read_rds(file.path(workingdir, "data", "metadata.rds"))
sites <- read_rds(file.path(workingdir, "data", "sites.rds"))
subpops <- read_rds(file.path(workingdir, "data", "subpop_color_coding.rds"))
phe_gr_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_GR50.rds"))
phe_fl_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_FL50.rds"))
k_full <- read_rds("~/Github/pvdiv-genome/tensite_twoyear/Kinship_van_Raden_630_individuals_SNPs_r2_20percent.rds")

@@

## Include just texas sites for greenup and just northern four sites.
e.g.:
for(p in 1){#seq_along(phe_dfs)){
  phe_v <- phe_lists[[p]]
  phe <- phe_dfs[[p]]

  for(i in 12:13){#seq_along(site_v)){ # may need to adjust below for h2_table
    for(j in 1:3){#seq_along(subpop_v)){
      for(k in seq_along(phe_v)){

## Model eight, texas, and north sites with a kinship : site interaction.
Then, find GxE and G proportions of variance.
```{r}
site_v <- list(TX1 = "TX1", TX2 = "TX2", TX3 = "TX3", OK = "OK", MO = "MO",
               NE = "NE", IL = "IL", MI = "MI", SD = "SD", eight_sites = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD"), nine_sites = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD"), tx_sites = c("TX1", "TX2", "TX3"), north_sites = c("MO", "NE", "MI", "SD"))
subpop_v <- list(Gulf = "Gulf", Midwest = "Midwest", Gulf_and_Midwest = c("Gulf", "Midwest"), Atlantic = "Atlantic", three_subpops = c("Atlantic", "Gulf", "Midwest"))
phe_fl <- c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl",
           "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d",
           "crain_7d")
phe_gr <- c("GR50", "DYLN", "cgdd_12c_jan2gr", "cgdd_8c_jan2gr", "tmax_18d", 
            "tmin_18d", "tave_18d", "cgdd_12c_18d", "tmax_10d", "tmin_10d",
            "tave_10d", "cgdd_12c_10d", "tmax_5d", "tmin_5d", "tave_5d",
            "cgdd_12c_5d")
phe_dfs <- list(phe_gr_df, phe_fl_df)
phe_lists <- list(phe_gr, phe_fl)
h2_table <- tibble()

for(p in seq_along(phe_dfs)){
  phe_v <- phe_lists[[p]]
  phe <- phe_dfs[[p]]

  for(i in c(10,12:13)){#seq_along(site_v)){ # may need to adjust below for h2_table
    for(j in 1:3){#seq_along(subpop_v)){
      for(k in seq_along(phe_v)){
        phe_single <- phe %>%
    left_join(sites, by = "SITE") %>%
    filter(manu_site %in% site_v[[i]] & SUBPOP %in% subpop_v[[j]]) %>%
    rename(phenotype = eval(phe_v[k])) %>%
    mutate(PLANT_ID = as_factor(PLANT_ID),
           SITE = as_factor(SITE),
           PLOT_GL = as_factor(PLOT_GL)) %>%
    as.data.frame()

  if(length(site_v[[i]]) > 1){  # need to add site as a random factor if 
    # there is more than one site included in the dataset.
    tryCatch({
     asr_out <- asreml(phenotype ~ 1,
                       random = ~vm(PLANT_ID, k_full) +
                         ~idv(SITE):vm(PLANT_ID, k_full),
                       residual = ~idv(units),
                       data = phe_single, 
                       workspace = "3gb")

@@

  if(i == 12 & j == 1 & k == 1){
    h2_table <- h2_est
  } else {
    h2_table <- add_row(h2_table, h2_est)
  }
  tryCatch({
      save_plot(filename=file.path(outputdir, paste0("ASReml_performance_",
                                                 names(site_v)[i], "_",
                                                 names(subpop_v)[j],
                                                 "_", phe_v[k], ".png")), 
            plot = plot(asr_out))
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
